### 2010-12-28 Documentation/atropos/atropos.tex
ENH:  A few minor edits.
git-svn-id: https://advants.svn.sourceforge.net/svnroot/advants@724 fd2da0a4-d968-48df-9cb5-d8c496287cbf

We also allow Atropos to address the bias field issue by incorporating
the recently developed N4 bias correction software \citep{Tustison2010} in an adaptive manner.  Coupled with the
registration \citep{Avants2010b} and template building 
\citep{Avants2010} already included in the ANTs toolkit, Atropos is a
versatile and powerful software tool which touches multiple aspects of
our brain processing pipeline from brain extraction
\citep{Avants2010a} to grey matter/white matter/cerebrospinal fluid
segmentation to label fusion and propagation for achieving a refined
cortical parcellation based on both prior information and
subject-specific image data.

@@

\subsection{Performance on Hammers Data}
Our prior work, \citep{Avants2010b}, showed that the majority vote
initialization provided to Atropos by ANTs template mapping is
competitive with \cite{Heckemann2006}.  The Atropos EM extension of
improved these results further.  However, the Atropos EM segmentation
performed significantly worse.  This is not surprising, in that
Atropos EM assumes that signal from the likelihood and MRF term is
valuable in improving the segmentation.  This assumption held for
amygdala and lateral ventricles among other areas.  However, in
pallidum and corpus callosum (the most significant areas with loss of
performance), this is not true.  We believe the explanation is that
the intensity varies within these structures and that a more complex
intensity model (or finer parcellation) would be needed here.  An
alternative solution would be to use boundary conditions for these
structures, as in the PriorLabelImage Atropos option.

>>>>

We also allow Atropos to address the bias field issue by incorporating
the recently developed N4 bias correction software \citep{Tustison2010} in an adaptive manner.  Coupled with the
registration \citep{Avants2011} and template building 
\citep{Avants2010} already included in the ANTs toolkit, Atropos is a
versatile and powerful software tool which touches multiple aspects of
our brain processing pipeline from brain extraction
\citep{Avants2010a} to grey matter/white matter/cerebrospinal fluid
segmentation to label fusion and propagation for achieving a refined
cortical parcellation based on both prior information and
subject-specific image data.

@@

\subsection{Performance on Hammers Data}
Our prior work, \citep{Avants2011}, showed that the majority vote
initialization provided to Atropos by ANTs template mapping is
competitive with \cite{Heckemann2006}.  The Atropos EM extension of
improved these results further.  However, the Atropos EM segmentation
performed significantly worse.  This is not surprising, in that
Atropos EM assumes that signal from the likelihood and MRF term is
valuable in improving the segmentation.  This assumption held for
amygdala and lateral ventricles among other areas.  However, in
pallidum and corpus callosum (the most significant areas with loss of
performance), this is not true.  We believe the explanation is that
the intensity varies within these structures and that a more complex
intensity model (or finer parcellation) would be needed here.  An
alternative solution would be to use boundary conditions for these
structures, as in the PriorLabelImage Atropos option.
